Spin canonical divisors of log stacky curves

### 2015-06-27 stacky_write_up/spin_cring.tex
ref fix, iffalse -> %, minor g1 table fix

\section{Inductive Lemmata}
\label{sec:induction}
First we present several lemmata which play a crucial role in the inductive step of the proof of the main theorem, Theorem ~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove Lemma ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3} which describe the generators and relations of $R_{D + \frac{\alpha}{\beta}P},$ given those in $R_D,$ where $X$ is a curve, $D \in \di X \otimes \BQ$ and  $\frac{\alpha}{\beta} \in \BQ.$ Next, in Subsection ~\ref{ssec:raise-orders}, we prove Lemma ~\ref{lem:raise-stacky-order}, which the generators and relations of the log spin canonical ring curve with signature $(g; e_1', \ldots, e_\tau'; 0)$ to that of the log spin canonical ring of a curve with a certain subset of the $e_i'$ incremented by $2$. While Lemma ~\ref{lem:sat-1} may be applied in a fairly general context, Lemma ~\ref{lem:raise-stacky-orders} is more specific to half-canonical divisors, although even Lemma ~\ref{lem:raise-stacky-orders} has certain generalizations, as noted in Remark ~\ref{rem:raise-fractional-order}

@@

\iffalse{
Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
\frac{\alpha}{\beta}$ is not a best lower approximation than we can
construct an element in degree $d$ with pole degree $c$ by either $y
_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
same conditions.  This forms a $k$-basis for $R_{\halfcan}$ over $R_{\halfcan'}$ and $y_1, \ldots, y_n$ generate $R_{\halfcan}$ over $R_{\halfcan'}$.  In particular, we see this generating set corresponds to the best positive approximations of $\frac{\alpha}{\beta}$.

Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$.  Choose an element of the form $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ as described in the previous paragraph, in degree with $d_l= 1$ and if 
$d_{l'}= 1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$. Specifically, we can 
successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1. For 
convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$. In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
is not well-defined, just pick an arbitrary element of $R_{\halfcan'}$ for $z_l$ ensuring that the 
expression still makes sense; in such cases we will always choose $a_l= 0$ so this choice 
is irrelevant, and only makes writing out cases more convenient. Therefore, we can write
\[
	x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
\]

\noindent
giving us a non-trivial relation with leading term $x_i y_j$. \todo{Explicitly state ordering at 
the beginning}

Similarly, suppose $y_i, y_j\in \{y_1, \ldots , y_{n - 1}\}$ with $1
< d_i$ and $j \ge i$ (that is, so $y_i y_j$ does not appear as a
basis element of the form described above: $y_n^0 y_j y_i u^0$). 
Choose the maximal $l$ such that $c_h \le c_i + c_j$; since $1 < d_i
\le d_j$, $(c_i + c_j) - c_j>\lfloor \frac{\alpha}{\beta}\rfloor$
so $c_{j + 1} < c_i + c_j$ meaning $c_h \ge c_{j + 1} > c_j$.
Furthermore, $c_i + c_j - c_h < \lfloor \frac{\alpha}{\beta} \rfloor
$ so either $c_h = c_i + c_j$ or there is some $h'$ such that $c_{h'}
= c_i + c_j - c_l$ and $d_{h'}= 1$. Since $\frac{c_h}{d_h}$ is a
best lower approximation of $\frac{\alpha}{\beta}$ with denominator
larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we
know that since $c_h\le c_i + c_j$ we must have $d_h < d_i + d_j$. 
Thus in the case with a $y_{l'}$ term we have $d_h + d_{h'} = d_h +
1 \le d_i + d_j$. That is to say, by choosing $b - d_i + d_j - a d_
h - 1$ we find (where $a \in \{0,1\}$ corresponding to if a $y_{h'}$
appears) that $y_h (y_h')^a u^b$ and $y_i y_j$ both lie in degree
$d_i + d_j$ with pole order $c_i + c_j$ at $P$. From here we can
follow a similar technique as in the previous paragraph to cancel
out poles of $y_i y_j$ at $P $ to find
\[
	y_i y_j -\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h} -\sum_l (y_l)^{s_l} (z_{l})^{a_l}
	u^{b_l}\in R_D
\]

\noindent
implying a relation with initial term $y_i y_j$.

Next, suppose $y_i, y_j \in \{y_1, \ldots , y_{n - 1}\}$ such that
$i \le j$, $d_j = d_i = 1$, and $d_{j + 1} = 1$ (i.e. $c_i, c_j \le
\lfloor \frac{\alpha}{\beta} - 1 \rfloor$). If $i > 1$ and then $y_
{j + 1} y_{i - 1}$ lies in the same degree as $y_i y_j$ (degree 2)
with the same pole order; following the same method as the previous
two paragraphs we find
\[
	y_i y_j - \gamma y_{i - 1} y_{j + 1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
\]

\noindent
Similarly if $i = 1$, then we get the same result using
\[
	y_i y_j - \gamma u y_{j + 1} - \sum_l y_l u^{b_l} \in R_D.
\]

\noindent
In both cases we deduce that $y_i y_j$ is an initial term of some relation.

Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i +
1}$ when $i = \lfloor \frac{\alpha}{\beta}\rfloor$. If $\beta = 1$,
then there are no relations with initial term a power of $y_i$
and we are immediately done. Otherwise, assuming $\beta \ne 1$, we
note that $c_i d_{i + 1} = c_{i + 1} d_i + 1 = c_{i + 1} + 1$. \todo
{reference to Evan's paper where he proves this} Therefore, if $i >
 1$ then $c_i^{d_{i + 1} + 1}$ and $c_{i - 1} c_{i + 1}$ both lie
in the $d_{i + 1} + 1$ degree with pole order $c_{i + 1} + 1$.
Following a similar technique to the previous paragraphs we find
\[
	(y_i)^{c_{i + 1} + 1} - y_{i + 1} y_{i - 1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
\]

\noindent
Similarly if $i = 1$ then
\[
	(y_i)^{c_{i + 1} + 1} - y_{i + 1}u - \sum_l (z_l)^{a_l} u^{b_l}.
\]

\noindent
In each case we demonstrate $(y_i)^{c_{i + 1} + 1}$ as the initial term of a relation.

Let $J$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$
generated by the initial terms described in the previous paragraphs
together with $\initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$.

We show that $J$ is in fact all of the initial ideal. Suppose
$f$ is a non-constant monomial that does not lie within $J$.
Further suppose $f$ does not lie in $k[u, x_1, \ldots, x_m]$. Then
there is some $y_i \mid f$. Since $f \not\in j$, we cannot have
some $x_j \mid f$ or else we would have $y_i x_j \mid f$
contradicting $f \not\in J$. Furthermore, if $y_l \mid f$ for $l <
i$, then we must have $d_l = 1$ or else $y_l y_i$ is an initial
element of a relation and divides $f$. If $d_i = 1$ as well, then
we must have $c_i = \lfloor \frac{\alpha} {\beta} \rfloor$, or else
$y_i y_l \in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{
\beta} \rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor + 1} + 1} \mid
f$. We observe that the remaining elements are precisely those of
the form $y_n^a y_i u^b$, $y_n^a z y_i u^b$, and $y_n^a z u^b$
which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots
, x_m, y_1, \ldots, y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.
Therefore, by dimension counting (in each degree), we see that $J$
is the initial ideal of $I$. 
}\fi

@@

\iffalse{
For any $x_j$, notice that $-\ord_P(y_4x_j)\le 1$. If it is non-positive, then it lies in $R_{\halfcan'}$ immediately giving us a relation with initial term $y_4x_j$. Otherwise, 
we can choose $A_j \in k$ and $w_j\in R_{\halfcan'}$ such that $y_4x_j -A_jy_3w_j$ has no pole at $P$ and thus lies in $R_{\halfcan'}$ giving us a desired relation. 
Similarly, we can find $B, C \in k$ such that $y_4^2 + B y_3^2 x_2+ Cy_3x_2x_3$ has no pole at $P$ and is thus in $R_D$. In both cases we induce a relation, with initial term described in the lemma's statement. Noting that any monomial is either a multiple of one of these initial terms, is a basis element (described above), or is in $R_D$, we see that these monomials in fact generate the initial ideal of $I$ over $\initial(I')$.
%Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}.
}\fi
\end{proof}

@@

\iffalse{
To see these generate $R'$ over $R$, note that $\dim_k R'_d - \dim_k R
_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
,$ elements of degree $d$ in the claimed basis of
~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
\rfloor $ and $b = d \bmod 3$, we have that the elements

\begin{align*}
	x_3^{a- 1}x_{3+b}, y_3x_3^{a-2}x_{3+b}, \ldots, y_3^ax_{3+b}, y_3^ay_{
3+b}
\end{align*}

\noindent
are precisely $a$ elements, which are all independent as they have
distinct pole orders at $P$. This completes part (a).

To show part (b), note that the generators in
~\ref{eqn:add_one_generator} are precisely a set of monomials which
generate $k[x, y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
suffices to show that all generators of $J$ lie in $in_\prec(I)$.

This follows, since there exist constants $A_{i,j} \in k$ for $4
\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
elements $w_{i,j} \in R'$ so that the following linear combinations
of elements lie in $R'$.

\begin{align*}
	&y_i x_j - A_{i,j} y_{i - 1}w_j \text{ so that } 4 \leq i \leq 5,3
	\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1 \\
	&y_4^2 + B_1 y_3 y_5 \\
	&y_4 y_5 + B_2 y_3^2 x_3 \\
	&y_5^2 + B_3 y_3^2 x_4
\end{align*}

\noindent
Of course, the initial terms of these elements are precisely the
generators of $J$, completing (b).
}\fi

@@

\begin{rem}
\label{rem:raise-fractional-order}
It is no coincidence that the proofs of Lemma ~\ref{lem:raise-stacky-orders} and \cite[Theorem 8.5.7]{vzb:stacky} are almost identical. In fact, the proofs of both results can easily be generalized generalized to the case of fractional canonical divisors, that is $L \in \di X$ with $nL \sim K$, for any $n \in \BZ_{\geq 1}$.
\end{rem}

@@

\begin{longtable}	{| c || c | c | c |}
	\hline
	L' & Generator Degrees & Degrees of Minimal Relations \\
	\hline
	\hline
	$0$ & $\{1\}$ & $\emptyset$ \\	\hline

@@

%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10, \ldots, e+2, e+3, e+5, e+7, \ldots, 2e-4\}$ \\	\hline
\end{longtable}
\begin{center}
\label{table:g-1-base}
Genus 1 base cases
\end{center}

@@

\begin{longtable}	{| c || c | c | c |}
	\hline
	L' & Generator Degrees & Degrees of Minimal Relations \\
	\hline
	\hline
	$P - Q$ & $\{2\}$ & $\emptyset$ \\	\hline

@@

%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10, \ldots, e+2, e+3, e+5, e+7, \ldots, 2e-4\}$ \\	\hline
\end{longtable}
\todo{Possibly add an autoincrement counter to deal with table numbering}
\begin{center}
\label{table:g-1-exceptional}
Genus 1 exceptional cases
\end{center}

@@

\begin{enumerate}
	\item[(a)] $\sigma_1 = (0; 3, 3, 11; 0), J_1 = \{3\}$
	\item[(b)] $\sigma_2 = (0; 3, 5, 9; 0), J_2 = \{3\}$
	\item[(c)] $\sigma_3 = (0; 3, 7, 7; 0), J_3 = \{2, 3\}$
	\item[(d)] $\sigma_4 = (0; 5, 5, 7; 0), J_4 = \{3\}$
	\item[(e)] $\sigma_5 = (0; 5, 7, 7; 0), J_5 = \{2, 3\}$
	\item[(f)] $\sigma_6 = (0; 7, 7, 7; 0), J_6 = \{1, 2, 3\}$
	\item[(g)] $\sigma_7 = (0; 3, 3, 3, 5; 0), J_7 = \{4\}$
	\item[(h)] $\sigma_8 = (0; 3, 3, 5, 5; 0), J_8 = \{3, 4\}$
	\item[(i)] $\sigma_9 = (0; 3, 5, 5, 5; 0), J_9 = \{2, 3, 4\}$
	\item[(j)] $\sigma_{10} = (0; 5, 5, 5, 5; 0), J_{10} = \{1, 2, 3, 4\}$
	\item[(k)] $\sigma_{11} = (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$
\end{enumerate}
\iffalse
\noindent
Furthermore, $R'$ satisfies the hypothesis of Lemma ~\ref
{lem:raise-stacky-order}(d), which asserts that for all $i \in J$, $e_i >
\deg z$ for any generator $z$ of $R'$ and if $R' = k[y, x]/I'$
(as defined in Lemma ~\ref{lem:raise-stacky-order}(c)) then
$in_\prec(I')$ is minimally generated by products of two monomials.
\fi
\end{lem}

@@

Therefore, the canonical ring $R'$ has presentation $R' =
k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}] / I$ with
initial ideal $in_\prec(I)$ generated by quadratics under grlex
with $x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$
%These quadratics must also determine minimal generators for $I$ by
%Lemma ~\ref{lem:minimal_quadratic}.
Thus, $R'$ is generated up to
degree $e = 7$ with relations up to degree $2e = 14$, as desired.s
\iffalse
We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
since $e_i = 9 > e$ for all $i \in J$.
\fi

@@

\iffalse
Through the application of two inductively adding 
points via Lemma ~\ref{lem:sat-3} and inductively raising
stabilizer orders via Lemma ~\ref{lem:raise-stacky-order},
we obtain Theorem ~\ref{thm:g-0-main} for any
log spin curve $(\sx, \Delta, L)$ with
signature $\sigma$ covered by this induction process.
In particular, this induction process covers all signatures $\sigma
= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
Before we prove the main theorem, we describe the cases not be
covered by induction.
\fi

>>>>

\section{Inductive Lemmata}
\label{sec:induction}
First we present several lemmata which play a crucial role in the inductive step of the proof of the main theorem, Theorem ~\ref{thm:main}. In Subsection ~\ref{ssec:add-points} we prove Lemma ~\ref{lem:sat-1}, ~\ref{lem:sat-2}, and ~\ref{lem:sat-3} which describe the generators and relations of $R_{D + \frac{\alpha}{\beta}P},$ given those in $R_D,$ where $X$ is a curve, $D \in \di X \otimes \BQ$ and  $\frac{\alpha}{\beta} \in \BQ.$ Next, in Subsection ~\ref{ssec:raise-orders}, we prove Lemma ~\ref{lem:raise-stacky-order}, which the generators and relations of the log spin canonical ring curve with signature $(g; e_1', \ldots, e_\tau'; 0)$ to that of the log spin canonical ring of a curve with a certain subset of the $e_i'$ incremented by $2$. While Lemma ~\ref{lem:sat-1} may be applied in a fairly general context, Lemma ~\ref{lem:raise-stacky-order} is more specific to half-canonical divisors, although even Lemma ~\ref{lem:raise-stacky-order} has certain generalizations, as noted in Remark ~\ref{rem:raise-fractional-order}

@@

%Thus, for a general $d$ (not necessarily less than $\beta$), if $\frac{c}{d} \le
%\frac{\alpha}{\beta}$ is not a best lower approximation than we can
%construct an element in degree $d$ with pole degree $c$ by either $y
%_n^a y_i u^b$, $y_n^a zy_iu^b$ or $y_n^a z u^b$ satisfying the
%same conditions.  This forms a $k$-basis for $R_{\halfcan}$ over $R_{\halfcan'}$ and $y_1, \ldots, y_n$ generate $R_{\halfcan}$ over $R_{\halfcan'}$.  In particular, we see this generating set corresponds to the best positive approximations of $\frac{\alpha}{\beta}$.
%Choose $x_i\in \{x_1, \ldots, x_m\}$ and $y_j\in \{y_1, \ldots, y_n\}$.  Choose an element of the form $y_n^a y_l u^b$ and $y_n^a y_l y_{l'} u^b$ as described in the previous paragraph, in degree with $d_l= 1$ and if 
%$d_{l'}= 1$ then $c_{l'} = \lfloor \frac{\alpha}{\beta} \rfloor$. Specifically, we can 
%successively subtract some $\gamma_l y_l u^{b_l}$, $\gamma_l y_l z_l u^{b_l}$, or $
%\gamma_l z_l$ with $y_l, z_l, b_l$ satisfying the same conditions as above and $\gamma_l
%\in k$ the element ensuring that the difference decreases in pole degree at $P$ by 1. For 
%convenience, we can combine these into the case $\gamma_l (y_l)^{s_l}(z_l)^{a_l}u^{b_l}$ 
%with $(s_l,a_l)\in \{(1,0),(1,1),(0,1)\}$. In the cases when $\frac{\alpha}{\beta}<1$ so $z_l$ 
%is not well-defined, just pick an arbitrary element of $R_{\halfcan'}$ for $z_l$ ensuring that the 
%expression still makes sense; in such cases we will always choose $a_l= 0$ so this choice 
%is irrelevant, and only makes writing out cases more convenient. Therefore, we can write
	%x_i y_j - \sum_{l} (y_l)^{s_l} (z_l)^{a_l} u^{b_l}\in R_D
%\noindent
%giving us a non-trivial relation with leading term $x_i y_j$. \todo{Explicitly state ordering at 
%the beginning}
%Similarly, suppose $y_i, y_j\in \{y_1, \ldots , y_{n - 1}\}$ with $1
%< d_i$ and $j \ge i$ (that is, so $y_i y_j$ does not appear as a
%basis element of the form described above: $y_n^0 y_j y_i u^0$). 
%Choose the maximal $l$ such that $c_h \le c_i + c_j$; since $1 < d_i
%\le d_j$, $(c_i + c_j) - c_j>\lfloor \frac{\alpha}{\beta}\rfloor$
%so $c_{j + 1} < c_i + c_j$ meaning $c_h \ge c_{j + 1} > c_j$.
%Furthermore, $c_i + c_j - c_h < \lfloor \frac{\alpha}{\beta} \rfloor
%$ so either $c_h = c_i + c_j$ or there is some $h'$ such that $c_{h'}
%= c_i + c_j - c_l$ and $d_{h'}= 1$. Since $\frac{c_h}{d_h}$ is a
%best lower approximation of $\frac{\alpha}{\beta}$ with denominator
%larger than those of $\frac{c_i}{d_i}$ and $\frac{c_j}{d_j}$, we
%know that since $c_h\le c_i + c_j$ we must have $d_h < d_i + d_j$. 
%Thus in the case with a $y_{l'}$ term we have $d_h + d_{h'} = d_h +
%1 \le d_i + d_j$. That is to say, by choosing $b - d_i + d_j - a d_
%h - 1$ we find (where $a \in \{0,1\}$ corresponding to if a $y_{h'}$
%appears) that $y_h (y_h')^a u^b$ and $y_i y_j$ both lie in degree
%$d_i + d_j$ with pole order $c_i + c_j$ at $P$. From here we can
%follow a similar technique as in the previous paragraph to cancel
%out poles of $y_i y_j$ at $P $ to find
	%y_i y_j -\gamma_h (y_h)^{s_h}(z_{h})^{a_h}u^{b_h} -\sum_l (y_l)^{s_l} (z_{l})^{a_l}
	%u^{b_l}\in R_D
%\noindent
%implying a relation with initial term $y_i y_j$. 
%Next, suppose $y_i, y_j \in \{y_1, \ldots , y_{n - 1}\}$ such that
%$i \le j$, $d_j = d_i = 1$, and $d_{j + 1} = 1$ (i.e. $c_i, c_j \le
%\lfloor \frac{\alpha}{\beta} - 1 \rfloor$). If $i > 1$ and then $y_
%{j + 1} y_{i - 1}$ lies in the same degree as $y_i y_j$ (degree 2)
%with the same pole order; following the same method as the previous
%two paragraphs we find
	%y_i y_j - \gamma y_{i - 1} y_{j + 1} - \sum_{l} (y_l)^{s_l} (z_l)^{a_l}u^{b_l}\in R_D.
%\noindent
%Similarly if $i = 1$, then we get the same result using
	%y_i y_j - \gamma u y_{j + 1} - \sum_l y_l u^{b_l} \in R_D.
%\noindent
%In both cases we deduce that $y_i y_j$ is an initial term of some relation.
%Finally, we examine the case (for $\alpha \ge \beta$) of $(y_i)^{i +
%1}$ when $i = \lfloor \frac{\alpha}{\beta}\rfloor$. If $\beta = 1$,
%then there are no relations with initial term a power of $y_i$
%and we are immediately done. Otherwise, assuming $\beta \ne 1$, we
%note that $c_i d_{i + 1} = c_{i + 1} d_i + 1 = c_{i + 1} + 1$. \todo
%{reference to Evan's paper where he proves this} Therefore, if $i >
 %1$ then $c_i^{d_{i + 1} + 1}$ and $c_{i - 1} c_{i + 1}$ both lie
%in the $d_{i + 1} + 1$ degree with pole order $c_{i + 1} + 1$.
%Following a similar technique to the previous paragraphs we find
	%(y_i)^{c_{i + 1} + 1} - y_{i + 1} y_{i - 1} - \sum_l (y_l)^{s_l}(z_l)^{a_l} u^{b_l}.
%\noindent
%Similarly if $i = 1$ then
	%(y_i)^{c_{i + 1} + 1} - y_{i + 1}u - \sum_l (z_l)^{a_l} u^{b_l}.
%\noindent
%In each case we demonstrate $(y_i)^{c_{i + 1} + 1}$ as the initial term of a relation. 
%Let $J$ be the ideal of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$
%generated by the initial terms described in the previous paragraphs
%together with $\initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$.
%We show that $J$ is in fact all of the initial ideal. Suppose
%$f$ is a non-constant monomial that does not lie within $J$.
%Further suppose $f$ does not lie in $k[u, x_1, \ldots, x_m]$. Then
%there is some $y_i \mid f$. Since $f \not\in j$, we cannot have
%some $x_j \mid f$ or else we would have $y_i x_j \mid f$
%contradicting $f \not\in J$. Furthermore, if $y_l \mid f$ for $l <
%i$, then we must have $d_l = 1$ or else $y_l y_i$ is an initial
%element of a relation and divides $f$. If $d_i = 1$ as well, then
%we must have $c_i = \lfloor \frac{\alpha} {\beta} \rfloor$, or else
%$y_i y_l \in I$; finally we can not have $(y_{\lfloor \frac{\alpha}{
%\beta} \rfloor})^{d_{\lfloor \frac{\alpha}{\beta} \rfloor + 1} + 1} \mid
%f$. We observe that the remaining elements are precisely those of
%the form $y_n^a y_i u^b$, $y_n^a z y_i u^b$, and $y_n^a z u^b$
%which are the elements of our chosen $k$-basis for $k[u, x_1, \ldots
%, x_m, y_1, \ldots, y_n]/I'$ over $k[u, x_1, \ldots, x_m]/I$.
%Therefore, by dimension counting (in each degree), we see that $J$
%is the initial ideal of $I$.

@@

%For any $x_j$, notice that $-\ord_P(y_4x_j)\le 1$. If it is non-positive, then it lies in $R_{\halfcan'}$ immediately giving us a relation with initial term $y_4x_j$. Otherwise, 
%we can choose $A_j \in k$ and $w_j\in R_{\halfcan'}$ such that $y_4x_j -A_jy_3w_j$ has no pole at $P$ and thus lies in $R_{\halfcan'}$ giving us a desired relation. 
%Similarly, we can find $B, C \in k$ such that $y_4^2 + B y_3^2 x_2+ Cy_3x_2x_3$ has no pole at $P$ and is thus in $R_D$. In both cases we induce a relation, with initial term described in the lemma's statement. Noting that any monomial is either a multiple of one of these initial terms, is a basis element (described above), or is in $R_D$, we see that these monomials in fact generate the initial ideal of $I$ over $\initial(I')$.
%Finally, (c) follows immediately from Lemma ~\ref{lem:minimal_quadratic}.

\end{proof}

@@

%To see these generate $R'$ over $R$, note that $\dim_k R'_d - \dim_k R
%_d = \lfloor \frac{d}{3} \rfloor,$ by Riemann--Roch. So, it
%suffices to show that we have precisely $\lfloor \frac{d}{3} \rfloor
%,$ elements of degree $d$ in the claimed basis of
%~\ref{eqn:add_one_generator}. Indeed, letting $a = \lfloor \frac{d}{3}
%\rfloor $ and $b = d \bmod 3$, we have that the elements
%
%\begin{align*}
	%x_3^{a- 1}x_{3+b}, y_3x_3^{a-2}x_{3+b}, \ldots, y_3^ax_{3+b}, y_3^ay_{
%3+b}
%\end{align*}
%
%\noindent
%are precisely $a$ elements, which are all independent as they have
%distinct pole orders at $P$. This completes part (a).
%
%To show part (b), note that the generators in
%~\ref{eqn:add_one_generator} are precisely a set of monomials which
%generate $k[x, y]/J$ over $k$. So, to show $J = in_\prec(I)$, it
%suffices to show that all generators of $J$ lie in $in_\prec(I)$.
%
%This follows, since there exist constants $A_{i,j} \in k$ for $4
%\leq i \leq 5,3 \leq j \leq m,$ elements $B_1,B_2,B_3 \in k$ and
%elements $w_{i,j} \in R'$ so that the following linear combinations
%of elements lie in $R'$.
%
%\begin{align*}
	%&y_i x_j - A_{i,j} y_{i - 1}w_j \text{ so that } 4 \leq i \leq 5,3
	%\leq j \leq m \text{ and } \deg w_j = \deg x_j + 1 \\
	%&y_4^2 + B_1 y_3 y_5 \\
	%&y_4 y_5 + B_2 y_3^2 x_3 \\
	%&y_5^2 + B_3 y_3^2 x_4
%\end{align*}
%
%\noindent
%Of course, the initial terms of these elements are precisely the
%generators of $J$, completing (b).

@@

\begin{rem}
\label{rem:raise-fractional-order}
It is no coincidence that the proofs of Lemma ~\ref{lem:raise-stacky-order} and \cite[Theorem 8.5.7]{vzb:stacky} are almost identical. In fact, the proofs of both results can easily be generalized generalized to the case of fractional canonical divisors, that is $L \in \di X$ with $nL \sim K$, for any $n \in \BZ_{\geq 1}$.
\end{rem}

@@

\begin{longtable}	{| c || c | c |}
	\hline
	L' & Generator Degrees & Degrees of Minimal Relations \\
	\hline
	\hline
	$0$ & $\{1\}$ & $\emptyset$ \\	\hline

@@

%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10, \ldots, e+2, e+3, e+5, e+7, \ldots, 2e-4\}$ \\	\hline
\end{longtable}

\begin{center}
\label{table:g-1-base}
Genus 1 base cases
\end{center}

@@

\begin{longtable}	{| c || c | c |}
	\hline
	L' & Generator Degrees & Degrees of Minimal Relations \\
	\hline
	\hline
	$P - Q$ & $\{2\}$ & $\emptyset$ \\	\hline

@@

%	$(1; e; 0)$ & $\{2, 3, 5, 7, 9, \ldots, e\}$ & $\{12\} \cup \{9,10, \ldots, e+2, e+3, e+5, e+7, \ldots, 2e-4\}$ \\	\hline
\end{longtable}
\todo{Possibly add an autoincrement counter to deal with table numbering}

\begin{center}
\label{table:g-1-exceptional}
Genus 1 exceptional cases
\end{center}

@@

\begin{enumerate}
	\item[(a)] $\sigma_1 = (0; 3, 3, 11; 0), J_1 = \{3\}$
	\item[(b)] $\sigma_2 = (0; 3, 5, 9; 0), J_2 = \{3\}$
	\item[(c)] $\sigma_3 = (0; 3, 7, 7; 0), J_3 = \{2, 3\}$
	\item[(d)] $\sigma_4 = (0; 5, 5, 7; 0), J_4 = \{3\}$
	\item[(e)] $\sigma_5 = (0; 5, 7, 7; 0), J_5 = \{2, 3\}$
	\item[(f)] $\sigma_6 = (0; 7, 7, 7; 0), J_6 = \{1, 2, 3\}$
	\item[(g)] $\sigma_7 = (0; 3, 3, 3, 5; 0), J_7 = \{4\}$
	\item[(h)] $\sigma_8 = (0; 3, 3, 5, 5; 0), J_8 = \{3, 4\}$
	\item[(i)] $\sigma_9 = (0; 3, 5, 5, 5; 0), J_9 = \{2, 3, 4\}$
	\item[(j)] $\sigma_{10} = (0; 5, 5, 5, 5; 0), J_{10} = \{1, 2, 3, 4\}$
	\item[(k)] $\sigma_{11} = (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$
\end{enumerate}

%\noindent
%Furthermore, $R'$ satisfies the hypothesis of Lemma ~\ref
%{lem:raise-stacky-order}(d), which asserts that for all $i \in J$, $e_i >
%\deg z$ for any generator $z$ of $R'$ and if $R' = k[y, x]/I'$
%(as defined in Lemma ~\ref{lem:raise-stacky-order}(c)) then
%$in_\prec(I')$ is minimally generated by products of two monomials.

\end{lem}

@@

Therefore, the canonical ring $R'$ has presentation $R' =
k[x_{7, 1}, x_{7, 2}, x_{5, 1}, x_{3, 1}] / I$ with
initial ideal $in_\prec(I)$ generated by quadratics under grlex
with $x_{7,1} \prec x_{7,2} \prec x_{5,1} \prec x_{3,1}$
%These quadratics must also determine minimal generators for $I$ by
%Lemma ~\ref{lem:minimal_quadratic}.
Thus, $R'$ is generated up to
degree $e = 7$ with relations up to degree $2e = 14$, as desired.s

%We can also see that $e_i > \deg z$ for any generator $z$ of $R'$
%since $e_i = 9 > e$ for all $i \in J$.

@@

%Through the application of two inductively adding 
%points via Lemma ~\ref{lem:sat-3} and inductively raising
%stabilizer orders via Lemma ~\ref{lem:raise-stacky-order},
%we obtain Theorem ~\ref{thm:g-0-main} for any
%log spin curve $(\sx, \Delta, L)$ with
%signature $\sigma$ covered by this induction process.
%In particular, this induction process covers all signatures $\sigma
%= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
%for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
%\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
%Before we prove the main theorem, we describe the cases not be
%covered by induction.
